Paper or report template

### 2024-11-02 manuscript/Manuscript.qmd
ms: test edits
talk update: split some slides, optimise layout, make presentation and course exercise same

---
title: "New paper template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: 
    embed-resources: true
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

[This]{.underline} is an R **Markdown** *document.* ^Markdown^ is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).

**text in bold** *italic* [underline]{.underline}

@@

You can add references either by referring to their id in the .bib file e.g., [@Marinkovi2020], or by switching to the visual editor (Cogwheel in the .Rmd menu -\> Use Visual Editor). [@Jokura_2023][@Jokura_2023][@Jacobs2023]

It is now a test to edit the text and see how the changes show up on GitHub.

Test of git show. And another test.

In the visual editor mode, go to 'Insert' -\> \@ Citation

You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]

The easiest way is to use the command line:

@@

curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.91258.1 >> references.bib
```

*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good campling location.

The references are stored in manuscript/references.bib (need to be defined in the Yaml header). This file will automatically updated when you insert a new reference through the Visual editor \> Insert \> Citations.

[@ozpolat2021][@Wu2020; @Saile2023; @Lohmann2023][@lohmann2001]

@@

## Results

Inserting Figures <!--# I don't agree here -->

You can add your figures into the rendered document. We saved the figures into /manuscript/figures or /manuscript/figure_supplements and can insert them from there. We use knitr::include_graphics for this. The title and legend can also be edited, as will as the width of the output figure. Test comment behaviour: <!--# Test comment for git show -->

@@

## Equations

@@

## Acknowledgements

We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by some funding agency.
We would like to thank all the Platynereis that gave their lives for science.

## Materials and Methods

@@

## References

>>>>

---
title: "Paper or report template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: 
    embed-resources: true
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

[This]{.underline} is a **Quarto** *document.* Quarto uses a simple ^Markdown^ formatting syntax for authoring HTML, PDF, and MS Word or .odt documents. For more details on using Quarto see <https://quarto.org/>.

Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.

@@

*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good sampling location.

# Results

## Adding references

You can add references either by referring to their id in the .bib file e.g., [@Marinkovi2020], or by switching to the visual editor (Cogwheel in the .Rmd menu -\> Use Visual Editor). [@Jokura_2023; @Jacobs2023]

In the visual editor mode, go to 'Insert' -\> \@ Citation
You can select a Zotero library, PubMed, CrossRef etc. and insert the citations. [@Jacobs2023]

One easy and techy way is to use the command line:

@@

curl -LH "Accept: application/x-bibtex" https://doi.org/10.7554/eLife.91258.1 >> references.bib

#make sure to use >> and not > otherwise you will overwrite your file!
```

The references are stored in manuscript/references.bib (needs to be defined in the Yaml header). This file will automatically updated when you insert a new reference through the Visual editor \> Insert \> Citations.

[@ozpolat2021; @Wu2020; @Saile2023; @Lohmann2023; @lohmann2001]

@@

Now edit the text, add a few references and press -> Render and see how the changes show up on the rendered document.
It is easier and faster to render your document to html. You will get a very nice dynamic layout that you can read in the browser (use Firefox). You can also render into pdf, but you need to install a version of latex for that. An easy alternative to generate a nice pdf is to open the html version in a browser (in this case Chrome gives the best results) and print to a pdf file.

## Inserting figures

You can add your figures into the rendered document. We saved the figures into /manuscript/figures or /manuscript/figure_supplements and can insert them from there. We use knitr::include_graphics for this. The title and legend can also be edited, as well as the width of the output figure.

@@

## Adding equations

@@

## Inserting comments

Inserting comments: <!--# I don't agree here -->
You can also use the visual editor and insert -> comment.

# Acknowledgements

We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by xy funding agency.

# Materials and Methods

@@

# References

### 2024-11-02 manuscript/Manuscript.tex
talk update: split some slides, optimise layout, make presentation and course exercise same

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{lineno}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={New paper template},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{New paper template}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\raggedright

@@

\ul{This} is an R \textbf{Markdown} \emph{document.}
\textsuperscript{Markdown} is a simple formatting syntax for authoring
HTML, PDF, and MS Word documents. For more details on using R Markdown
see \url{http://rmarkdown.rstudio.com}.

\textbf{text in bold} \emph{italic} \ul{underline}

@@

You can add references either by referring to their id in the .bib file
e.g., (Marinković et al., 2019), or by switching to the visual editor
(Cogwheel in the .Rmd menu -\textgreater{} Use Visual Editor). {[}Jokura
et al. (2023){]}(Jokura et al., 2023)(Jacobs and Ryu, 2023)

It is now a test to edit the text and see how the changes show up on
GitHub.

Test of git show.

In the visual editor mode, go to `Insert' -\textgreater{} @ Citation

You can select a Zotero library, PubMed, CrossRef etc. and insert the
citations. (Jacobs and Ryu, 2023)

The easiest way is to use the command line:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{curl} \AttributeTok{{-}LH} \StringTok{"Accept: application/x{-}bibtex"}\NormalTok{ https://doi.org/10.7554/eLife.91258.1 }\OperatorTok{\textgreater{}\textgreater{}}\NormalTok{ references.bib}
\end{Highlighting}
\end{Shaded}

\emph{Platynereis dumerilii} is a marine annelid\ldots{} (Ozpolat et
al., 2021)

@@

{[}Ozpolat et al. (2021){]}(Lohmann et al., 2023; Saile et al., 2023; Wu
et al., 2020)(Lohmann et al., 2001)

@@

\subsection{Results}\label{results}

Inserting Figures

@@

\subsection{Equations}\label{equations}

@@

\subsection{Acknowledgements}\label{acknowledgements}

We would like to thank the Jekely lab for the R project template
(\url{https://github.com/JekelyLab/new_paper_template}) we used to write
this paper. This work was funded by \ldots{}

\subsection{Materials and Methods}\label{materials-and-methods}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3000}}@{}}
\caption{Grid Table example}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
a & b & c & d & e \\
d & & & & \\
\end{longtable}

@@

\subsection{References}\label{references}

>>>>

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{lineno}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Paper or report template},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Paper or report template}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\raggedright

@@

\ul{This} is a \textbf{Quarto} \emph{document.} Quarto uses a simple
\textsuperscript{Markdown} formatting syntax for authoring HTML, PDF,
and MS Word or .odt documents. For more details on using Quarto see
\url{https://quarto.org/}.

Here is our abstract. We discovered that medaka fish can eat
Arabidpopsis shoop apical meristeme cells to regulate energy metabolism
(data not shown). Here is some \textbf{text in bold} \emph{italic}
\ul{underline} and \textsuperscript{superscript}.

@@

\emph{Platynereis dumerilii} is a marine annelid\ldots{} (Ozpolat et
al., 2021). It is also the coolest model organism. It lives in shallow
sea on seagrass. Ischia is a good sampling location.

\section{Results}\label{results}

\subsection{Adding references}\label{adding-references}

You can add references either by referring to their id in the .bib file
e.g., (Marinković et al., 2019), or by switching to the visual editor
(Cogwheel in the .Rmd menu -\textgreater{} Use Visual Editor). (Jacobs
and Ryu, 2023; Jokura et al., 2023)

In the visual editor mode, go to `Insert' -\textgreater{} @ Citation You
can select a Zotero library, PubMed, CrossRef etc. and insert the
citations. (Jacobs and Ryu, 2023)

One easy and techy way is to use the command line:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{curl} \AttributeTok{{-}LH} \StringTok{"Accept: application/x{-}bibtex"}\NormalTok{ https://doi.org/10.7554/eLife.91258.1 }\OperatorTok{\textgreater{}\textgreater{}}\NormalTok{ references.bib}

\CommentTok{\#make sure to use \textgreater{}\textgreater{} and not \textgreater{} otherwise you will overwrite your file!}
\end{Highlighting}
\end{Shaded}

@@

(Lohmann et al., 2023; Lohmann et al., 2001; Ozpolat et al., 2021; Saile
et al., 2023; Wu et al., 2020)

@@

Now edit the text, add a few references and press -\textgreater{} Render
and see how the changes show up on the rendered document. It is easier
and faster to render your document to html. You will get a very nice
dynamic layout that you can read in the browser (use Firefox). You can
also render into pdf, but you need to install a version of latex for
that. An easy alternative to generate a nice pdf is to open the html
version in a browser (in this case Chrome gives the best results) and
print to a pdf file.

\subsection{Inserting figures}\label{inserting-figures}

@@

\subsection{Adding equations}\label{adding-equations}

@@

\subsection{Inserting comments}\label{inserting-comments}

Inserting comments: You can also use the visual editor and insert
-\textgreater{} comment.

\section{Acknowledgements}\label{acknowledgements}

We would like to thank the \href{https://github.com/JekelyLab}{Jekely
lab} for the \href{https://github.com/JekelyLab/new_paper_template}{R
project template} we used to write this paper. This work was funded by
xy funding agency.

\section{Materials and Methods}\label{materials-and-methods}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3000}}@{}}
\caption{Grid Table example}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Col1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col2
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Col5
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
a & b & c & d & e \\
d & & & & \\
v & n & f & & f \\
\end{longtable}

@@

\section{References}\label{references}
